\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-11-14 manuscript.Rmd
adding country/timezone information in the participants text as bullet points

# create descriptive table for the demographic vars (excluding tz & Country) with gtsummary
desctable.data %>%
  tbl_summary(
    by = IncludedInCFA,
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
    digits = all_continuous() ~ 2,
    label = list(slypos_demographics_age ~ "Age",
                 slypos_demographics_sex.factor ~ "Sex",
                 slypos_demographics_gender.factor ~ "Gender-Variant Identity",
                 slypos_demographics_language.factor ~ "Native English Speaker",
                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
                 slypos_demographics_school.factor ~ "Occupational setting"
                 ),
    missing = "no"
    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
modify_header(label ~ "**Variable**") %>% modify_caption("Dempgraphics") -> desc_table

@@

@@

Table 1 summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. XX participants were excluded from analysis due to not passing at least one of the "attention check" items. For exploring initial factor structure (EFA) , a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per parameter is required to earn trustworthiness of the result. Our sample size exceeds these requirements: Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1. EFA Sample",])`) and confirmatory factor analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2. CFA Sample",])`). The EFA sample included participants filling out the questionnaire from 17.05.2021 to XX.XX.XXXX , whereas participants who filled out the questionnaire from YY.YY.YYYY to 03.09.2021 were included in the CFA analysis. Participants indicated filling out the online survey from a diverse range of geographic locations. The four most common geographic locations included:

`r kable(head(summary(descriptives.data$slypos_demographics_tz.factor), 4), format = "latex")`

@@

Age among all participants ranged from `r min(desctable.data$slypos_demographics_age)` years to `r max(desctable.data$slypos_demographics_age)` years [EFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age [Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`]. In total `r desc_tibble[3,2]` of the participants indicated female sex [EFA: `r desc_tibble[3,3]`; CFA: `r desc_tibble[3,4]`], `r desc_tibble[4,2]` indicated male [EFA: `r desc_tibble[4,3]`; CFA: `r desc_tibble[4,4]`] and `r desc_tibble[5,2]` indicated other sex [EFA: `r desc_tibble[5,3]`, CFA: `r desc_tibble[5,4]`]. Overall, `r desc_tibble[6,2]` [EFA: `r desc_tibble[6,3]`; CFA: `r desc_tibble[6,4]`] participants indicated a gender-variant identity. In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers. For their "Occupational Status", more than half of the overall sample reported that they currently work [Overall: `r desc_tibble[9,2]`; EFA: `r desc_tibble[9,3]`; CFA: `r desc_tibble[9,4]`], whereas `r desc_tibble[10,2]` [EFA: `r desc_tibble[10,3]`; CFA: `r desc_tibble[10,4]`] reported that they go to school and `r desc_tibble[11,2]` [EFA: `r desc_tibble[11,3]`; CFA: `r desc_tibble[11,4]`] responded that they do "Neither". With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` [EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`] of the participants indicated that they were in a home office/ home schooling setting., while `r desc_tibble[14,2]` overall [EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`] reported face-to-face work/schooling. Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or indication)" response option. We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's $\chi^2$ test for all other categorical variables via the gtsummary R package's "add_p" function [@sjoberg2021] . The p-values were corrected for multiple testing applying false discovery rate (FDR) via the "add_q" function of the same package. After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* ≥ `r min(desc_tibble$"**q-value**", na.rm=T)` , indicating equivalence).

>>>>

# create descriptive table for the demographic vars (excluding tz & Country) with gtsummary
desctable.data %>%
  tbl_summary(
    by = IncludedInCFA,
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
    digits = all_continuous() ~ 2,
    label = list(slypos_demographics_age ~ "Age",
                 slypos_demographics_sex.factor ~ "Sex",
                 slypos_demographics_gender.factor ~ "Gender-Variant Identity",
                 slypos_demographics_language.factor ~ "Native English Speaker",
                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
                 slypos_demographics_school.factor ~ "Occupational setting"
                 ),
    missing = "no"
    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
modify_header(label ~ "**Variable**") %>% modify_caption("Demographics") -> desc_table

@@

#summarise country/time zone data

descriptives.data%>%
  tbl_summary(
    label = slypos_demographics_tz.factor ~ "Time zone - Country",
    statistic = list(all_categorical() ~ "{n} ({p}%)"),
    missing = "no",
    sort = all_categorical() ~ "frequency",
    include = "slypos_demographics_tz.factor"
  )  %>% bold_labels() %>% 
  modify_header(label ~ "") %>%
  as_tibble(format = 'pipe') -> tz_tibble

@@

Table 1 summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. XX participants were excluded from analysis due to not passing at least one of the "attention check" items. For exploring initial factor structure (EFA) , a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per parameter is required to earn trustworthiness of the result. Our sample size exceeds these requirements: Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1. EFA Sample",])`) and confirmatory factor analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2. CFA Sample",])`). The EFA sample included participants filling out the questionnaire from 17.05.2021 to XX.XX.XXXX , whereas participants who filled out the questionnaire from YY.YY.YYYY to 03.09.2021 were included in the CFA analysis. Participants indicated filling out the online survey from a diverse range of geographic locations. The ten most common geographic locations included:

- `r tz_tibble[2,1]`:     `r tz_tibble[2,2]` 
- `r tz_tibble[3,1]`:     `r tz_tibble[3,2]`
- `r tz_tibble[4,1]`:     `r tz_tibble[4,2]`
- `r tz_tibble[5,1]`:     `r tz_tibble[5,2]`
- `r tz_tibble[6,1]`:     `r tz_tibble[6,2]`
- `r tz_tibble[7,1]`:     `r tz_tibble[7,2]`
- `r tz_tibble[8,1]`:     `r tz_tibble[8,2]`
- `r tz_tibble[9,1]`:     `r tz_tibble[9,2]`
- `r tz_tibble[10,1]`:    `r tz_tibble[10,2]`
- `r tz_tibble[11,1]`:    `r tz_tibble[11,2]`

@@

Age among all participants ranged from `r min(desctable.data$slypos_demographics_age)` years to `r max(desctable.data$slypos_demographics_age)` years [EFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age [Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`]. In total `r desc_tibble[3,2]` of the participants indicated female sex [EFA: `r desc_tibble[3,3]`; CFA: `r desc_tibble[3,4]`], `r desc_tibble[4,2]` indicated male [EFA: `r desc_tibble[4,3]`; CFA: `r desc_tibble[4,4]`] and `r desc_tibble[5,2]` indicated other sex [EFA: `r desc_tibble[5,3]`, CFA: `r desc_tibble[5,4]`]. Overall, `r desc_tibble[6,2]` [EFA: `r desc_tibble[6,3]`; CFA: `r desc_tibble[6,4]`] participants indicated a gender-variant identity. In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers. For their "Occupational Status", more than half of the overall sample reported that they currently work [Overall: `r desc_tibble[9,2]`; EFA: `r desc_tibble[9,3]`; CFA: `r desc_tibble[9,4]`], whereas `r desc_tibble[10,2]` [EFA: `r desc_tibble[10,3]`; CFA: `r desc_tibble[10,4]`] reported that they go to school and `r desc_tibble[11,2]` [EFA: `r desc_tibble[11,3]`; CFA: `r desc_tibble[11,4]`] responded that they do "Neither". With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` [EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`] of the participants indicated that they were in a home office/ home schooling setting, while `r desc_tibble[14,2]` overall [EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`] reported face-to-face work/schooling. Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or on vacation)" response option. We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's $\chi^2$ test for all other categorical variables via the gtsummary R package's "add_p" function [@sjoberg2021] . The p-values were corrected for multiple testing applying false discovery rate (FDR) via the "add_q" function of the same package. After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* ≥ `r min(desc_tibble$"**q-value**", na.rm=T)` , indicating equivalence).
